Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
add the result table

\section{Results}
\label{threats}
TODO
\subsection{Qualitative}
TODO
\subsection{Quantitative}
TODO

>>>>

\section{Results}
\label{threats}
\begin{table*}[ht]
\caption{Number of Smells}
\centering
\begin{tabular}{|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|}
 \hline\hline
Module Name & Num Files & Nested Toggle \#Smells & Spread Toggle \#Smells & Combinatorial Toggle \#Smells &  Dead Toggle \#Smells & Average time to scan/Smell \\ \hline

Base & 749 & 1 & 5 & 4  & 0 & 1556013 ms \\ \hline
UI & 1501 & 2 & 1 & 0  & 0 & 888080 ms \\ \hline
Net & 1534 & 16 & 0 & 9  & 0 & 927508 ms \\ \hline
Media & 746 & 16 & 0 & 9  & 0 & 370563 ms \\ \hline
ppapi & 563 & 0 & 0 & 0  & 0 & 944816 ms \\ \hline
ash & 502 & 1 & 1 & 0  & 0 & 390563 ms \\ \hline
chrome & 6105 & 109 & 31 & 24  & 0 & 2468547 ms \\ \hline

\end{tabular}
\label{table:chrome-result-data}
\end{table*}

\subsection{Qualitative}
TODO
\subsection{Quantitative}
TODO
